Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-08-16 Manuscript/manuscript.tex
Figure PC-PS interaction contains the correct experimental series now. Data with both Na+ and K+ counterions plotted. Few details in text updated, e.g. the main message.

\begin{abstract} 
	\emph{Adapt abstract to the final message: properties of POPS-containing bilayers -or- ECC-concept applicability?}

@@

\subsection{Electrometer concept: cationic and anionic amphiphilic molecules}

\todo{SAMULI: This section should be titled something like ''PS-PC headgroup interactions in mixtures'',
unless we actually run simulations with anionic amphiphilic molecules.}

@@

\begin{figure}[htb!] 
  \centering 
  \includegraphics[width=\figwidthsmall]{../Fig/l17/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/l17/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    Changes of the head group order parameters of a POPC:POPS 5:1 bilayer as a function of PS content
    Experimental points have inherent systematic error, as they come from different experiments.
    A complete series of points can be found (?) in \cite{roux90} -- which is to be added to the plot.
  } 
\todo{SAMULI: It would be probably better to show also here the Lipid17 and ECC results in the same 
  plot as done in the other figures.}
\end{figure}

@@

>>>>

\begin{abstract}

\textbf{Main message: 
ECC generally improves interaction and structure of both neutral and charged molecules. 
Polarizability is necessarry for accurate simulations of cellular membranes at physiological ionic conditions.}

@@

\subsection{Interactions between PC and PS head groups in mixed PC:PS bilayers}

@@

\begin{figure}[htb!] 
  \centering 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_nacl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPC_kcl.pdf} 
  \includegraphics[width=\figwidthsmall]{../Fig/order_parameters_changes_A-B_PC-PS_mix_POPS_kcl.pdf} 
  \caption{\label{fig:delta_ordPar_NaCl_PC-PS_mix} 
    Changes of the head group order parameters of a POPC:POPS (5:1) bilayer as a function of PS content
    with \ce{Na^+} and \ce{K^+} counterions from simulations with ECC-lipids and Lipid17 \cite{lipid17-future} 
    and experiments (only \ce{Na^+} counterions). \cite{roux90}. 
    The underestimated response of ECC-lipids with \ce{Na^+} counterions 
    is likely due to a still slightly overestimated binding affinity of \ce{Na^+} to the phospholipids,
    which is corroborated by the series with \ce{K^+} counterions (lower affinity than \ce{Na^+}),
    where the response is closer to the experiment (which uses only \ce{Na^+} counterions). 
    Experimental points for POPS inherently contain larger systematic error, 
    as they come from independent experiments.
  } 
\todo{Josef: Simulation at 50:50 PC:PS might be useful for this plot (PC-PS interactions). 
Now it may make an impression, that we are consciously avoiding it. }
\end{figure}

@@

\textbf{This will be exemplified on POPS throughout this paper and, hence, it does not require additional section. }
